\section{Acknowledgements}
R.~ Torre and P.~Fox thank Dropbox, but not git.



The research of  A.~Aboubrahim  and P.~Nath was supported in part by NSF Grant PHY-1620575.

The research of J.~Kalinowski and W.~Kotlarski was supported in part by 
the National Science Centre, Poland,  HARMONIA project under contract UMO-2015/18/M/ST2/00518 (2016-2019).

We would like to thank Matthew Low and Lian-Tao Wang for discussions. This work was supported in part by the U.S.~Department of Energy under grant No.~DE-FG02- 95ER40896 and by the PITT PACC. T.~ Han also acknowledges the hospitality of the Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1607611.

%S. V. Chekanov$^1$, J. T. Childers$^2$, J. Proudfoot$^3$, R.Wang$^4$, D. Frizzell
The submitted manuscript has been created by UChicago Argonne, LLC,
Operator of Argonne National Laboratory (``Argonne'').
Argonne, a U.S. Department of Energy Office of Science laboratory,
is operated under Contract No. DE-AC02-06CH11357.
This research was made possible by an allocation of computing time through the ASCR Leadership Computing Challenge (ALCC) program. This research used resources of the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231.

%B. Allanach$^1$, D. Bhatia$^2$ and A. Iyer
This work has been partially supported by STFC consolidated grants ST/L000385/1, ST/P000681/1.

%B. Allanach, B. Gripaios, T. Tevong You
This work has been partially supported by STFC consolidated grants ST/L000385/1 and ST/P000681/1.

%M. Altakach$^1$, T. Jezo$^2$, M. Klasen
The work of M.~Klasen has been supported by the BMBF under contract 05H15PMCCA and the DFG through the Research Training Network 2149
``Strong and weak interactions - from hadrons to dark matter''.
T.~Jezo was supported by the Swiss National Science Foundation~(SNF) under contracts BSCGI0-157722 and CRSII2-160814.

%S. De Curtis$^a$, L. Delle Rose$^{a}$, S. Moretti$^{b,c}$, A. Tesi$^{a}$, K. Yagyu
SM is funded in part through the NExT Institute and the STFC CG ST/P000711/1.

%Dario Buttazzo$^{a,1}$, Filippo Sala$^{b,2}$, Andrea Tesi
The work of F.S. is partly supported by a PIER Seed Project funding (Project ID PIF-2017-72).

%S. Biswas, E. Gabrielli, M. Heikinheimo, B. Mele
The work of Matti Heikinheimo has been supported by the Academy of Finland, Grant NO. 31013